---
title: "GLM Group 5 GLM Main"
output:
  html_document: default
  pdf_document: default
---

**Step 0: Load the data**

```{r setup, include=FALSE}
mydata <- read.csv('C:/Users/z725312/Documents/datascience/GLMG5/data/Cellphone-1.csv', header=TRUE)
names(mydata)
```

```{r}
#Factorizing relavent colunmns
mydata$Churn <- factor(mydata$Churn, levels = c(0,1), labels = c("No", "Yes"))
mydata$ContractRenewal <- factor(mydata$ContractRenewal, levels = c(0,1), labels = c("No", "Yes"))
mydata$DataPlan <- factor(mydata$DataPlan, levels = c(0,1), labels = c("No", "Yes"))
#mydata$CustServCalls <- factor(mydata$CustServCalls, levels = c(0,1,2,3,4,5,6,7,8,9), labels = c(0,1,2,3,4,5,6,7,8,9))
```

```{r}
mydata$AccountWeeks = mydata$AccountWeeks/100
mydata$DayMins = mydata$DayMins/60
mydata$DayCalls = mydata$DayCalls/100
mydata$MonthlyCharge = mydata$MonthlyCharge/10
```


```{r}
#Splitting dataset:
library(caTools)
set.seed(123)
split=sample.split(mydata$Churn,SplitRatio =0.7)
dev_set=subset(mydata,split==TRUE)
test_set=subset(mydata,split==FALSE)
```


**Step 1: Overall Significance of the logistics regression to test applicabiliy**

```{r}
logit <- glm(Churn~., data=dev_set, family = binomial)
library(lmtest)
lrtest(logit)
```

Interpretation:
The overall test of the model significance based on chisq test above is overwhelmingly significant indicating the likelihood of loyalty depends upon Brand, Products and Shopping

**Step 2: Macfadden R2 and interpretation**

```{r}
library(pscl)
pR2(logit)
```

Interpretation:
Based on McFadden R2, we conculde that 43.56 percent of the uncertainity of the intercept only model (model 2) has been explained by the Full Model (model 1). 

**Step 3: Individual Coefficient's significance and interpretation**

```{r}
summary(logit)
```

Interpretation:
Only attitude toward brand is overwhelmingly significant in explaining loyalty (Look at Pr(>|z|) which is the p-value).  

** Step 4: Explainatory power of Odds Ratio **

Odds:
```{r}
round(exp(coef(logit)), 3)
```

Probability:
```{r}
round(exp(coef(logit))/(1+exp(coef(logit))), 3) * 100
```

If Odds is more than 1, the probability of influence will be more than 50. So we cannot ignore the variables with Odds more than 1.

** Step 5: Confustion Matrix (Misclassification Matrix) **

```{r}
prediction <- predict(logit, type = "response", data = dev_set)
cutoff=floor(prediction > 0.5)
table(Actual = dev_set$Churn, Predicted= cutoff)
```

** Step 6: ROC Plot - Receiver Operating Characteristics **

```{r}
library("ROCR")    
pred <- prediction(prediction, dev_set$Churn)    
perf <- performance(pred, measure = "tpr", x.measure = "fpr")     
plot(perf, col=rainbow(7), main="ROC curve Admissions", xlab="Specificity", 
     ylab="Sensitivity") 
```

```{r}
auc <- performance(pred,"auc"); 
as.numeric(auc@y.values)
```


Prediction
```{r}
pred_test <- predict(logit, type = "response", newdata = test_set)
cutoff1=floor(pred_test > 0.5) 
table(Actual=test_set$Churn, predicted = cutoff1)
```

```{r}
library(caret)
cm <- data.frame(Churn = test_set$Churn, cutoff1)
cm$cutoff1 = as.factor(cm$cutoff1)
confusionMatrix(as.numeric(cm$Churn)-1, as.numeric(cm$cutoff1)-1)
```

```{r}
auc_test_result <- performance(pred_test_result,"auc"); 
as.numeric(auc_test_result@y.values)
```


Prediction with cutoff
```{r}
pred_test_cutoff <- predict(logit, type = "response", newdata = test_set)
cutoff2=floor(pred_test_cutoff > 0.077) 
table(Actual=test_set$Churn, predicted = cutoff2)
```


```{r}
library(caret)
cm <- data.frame(Churn = test_set$Churn, cutoff2)
cm$cutoff2 = as.factor(cm$cutoff2)
confusionMatrix(as.numeric(cm$Churn)-1, as.numeric(cm$cutoff2)-1)
```

